\documentclass[a4paper,11pt]{article}

\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{geometry}

% Font
\usepackage{charter}

% Adjust margins
\geometry{left=0.5in, right=0.5in, top=0.5in, bottom=1in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Remove page numbering
\pagenumbering{gobble}

%-------------------------
% Custom commands
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}
\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small\textbf{#1} & #2 \\
  \end{tabular*}\vspace{-8pt}
}

\newcommand{\chref}[3]{\href{#2}{\color{#1}{\underline{#3}}}}

\setlist{leftmargin=16pt}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{center}
  \textbf{\Huge Fadil Muh} \\
  \vspace{2mm}
  \begin{tabular}{c c}
    \chref{blue}{mailto:fadilmuh2002@gmail.com}{fadilmuh2002@gmail.com}
    \hspace{4pt}$|$\hspace{4pt}
    \chref{blue}{https://github.com/fadilmuh22}{github.com/fadilmuh22}
    \hspace{4pt}$|$\hspace{4pt}
    \chref{blue}{https://linkedin.com/in/fadilmuh22}{linkedin.com/in/fadilmuh22}
  \end{tabular}
\end{center}

%-----------Experiences-----------
\section{Experiences}
\begin{itemize}[leftmargin=0.15in, label={}]
    \resumeSubheading{React Developer \& Flutter Developer}{2020 - 2022}{SoftwareSeni}{}
    \begin{itemize}
      \item Enhanced and maintained Software Delivery Platform web app.
      \item Architected and Developed an Online Health Check-ups mobile app.
      \item Develop and maintain web applications for enterprise solutions in education sectors.
      \item Worked collaboratively with a diverse team of colleagues from various cultural backgrounds.
      \item Contributed to the development and maintenance of monorepo and microservices-based architectures.
    \end{itemize}\vspace{-4pt}

    \resumeSubheading{Full-Stack Developer}{2022 - 2024}{Freelance}{}
    \begin{itemize}
      \item Developed Android and IOS applications and deployed them to the Play Store and App Store.
      \item Implement design to a mobile application and integrate it with backend service.
      \item Integrate the application with Firebase for authentication service.
      \item Quick ISK. Quick accreditation prediction for Telkom University. Developed for Android and IOS using Flutter.
      \item My Garden. Pest reporting application for PT Perkebunan Nusantara. Developed for Android using Flutter.
      \item Ampuh. A reporting app for more than 5000 engineers. Migrated the app framework from Ionic 3 to 5.
    \end{itemize}\vspace{-4pt}

    \resumeSubheading{React Developer \& Flutter Developer Intern}{Sep 2021 - Dec 2021}{Sagara Technology}{}
    \begin{itemize}
      \item Coded Crowdfunding web app frontend with React.
      \item Implement web design to a reusable component.
      \item Integrate components to use REST API service using Redux, React Hook, and Axios.
      \item Built the Crowdfunding mobile app from scratch using Flutter.
      \item Used Bloc architecture for the mobile app.
    \end{itemize}\vspace{-4pt}

\end{itemize}

%-----------Projects-----------
\section{Projects}
\begin{itemize}[leftmargin=0.15in, label={}]
    \resumeProjectHeading{Ecoviary}{March 2024}{}{}
    \begin{itemize}
      \item Developed Ecoviary. A smart poultry farming innovation mobile app.
      \item Coded the backend to manage real-time data and interact with IOT device.
      \item Deployed the backend to the Digitalocean server using Ansible and Terraform.
    \end{itemize}\vspace{-8pt}

    \resumeProjectHeading{Dapur Pasar}{December 2022}{}{}
    \begin{itemize}
      \item Worked with a team of 4 people to develop a marketplace mobile application.
      \item Develop and Built the mobile app for users, drivers, and partners using IONIC and Angular.
      \item Architected the app using MVC and Dependency Injection.
      \item Integrate Real-time tracking order using WebSocket.
      \item Coded the backend for WebSocket in Nodejs.
    \end{itemize}\vspace{-8pt}

    \resumeProjectHeading{Aksesku}{August 2022}{}{}
    \begin{itemize}
      \item Develop mobile apps for taking attendance in a University using React Native.
      \item Integrate with API to capture and send attendance data.
      \item Working closely with team lead to maintain clean code and code readability.
    \end{itemize}\vspace{-8pt}

    \resumeProjectHeading{Jastis LMS}{April 2021}{}{}
    \begin{itemize}
      \item Led and worked with a team of 7 people to develop a multi-platform LMS application.
      \item Built the mobile app using Flutter.
      \item Architected the app using MVC and Dependency Injection.
      \item Integrate Rest API and Firebase for push notification.
      \item Coded the backend using Laravel and MongoDB.
      \item Rebuilt and published the Laravel-FCM to be used in the backend service.
    \end{itemize}\vspace{-8pt}

    \resumeProjectHeading{IoT-based Attendance Device and Application}{September 2020}{}{}
    \begin{itemize}
      \item Created the CMS and the Backend for communicating with the Attendance device using REST API.
      \item Integrate mailing service to send QR code tickets for attendance.
      \item Coded the microcontroller device using C++ for taking temperature and attendance ID from the QR code.
    \end{itemize}\vspace{-8pt}

\end{itemize}

%-----------Skills-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{
    \item{
        \vspace{1mm}
        \textbf{Languages}{: Typescript, JavaScript, Node, Go, Python, Dart, Kotlin} \\
        \textbf{Framework \& Libraries}{: React, Nest, Next, Angular, Vue, Express,  PostgreSQL, MySQL, Flutter, Echo } \\
        \textbf{Other}{: Ansible, Terraform, Docker, Git, Restful API, Tailwind Cloud Computing, Machine Learning, DevSecOps} \\
      }
    }
\end{itemize}

%-----------Education-----------
\section{Education}
\begin{itemize}[leftmargin=0.15in, label={}]
    \resumeSubheading{SMKN 4 Bandung}{2018 - 2021}{Software Engineering}{}
\end{itemize}

\end{document}
